The error when inferring phylogenies with incipient species by a Birth-Death model

### 2018-04-11 article.tex
Violin plot

The data set produced by this exploratory research will consist out of two files:
one containing raw data, the other summarized data. 
A data file should be convenient to handle, thus as an upper limit for this data set's size, 
we use the maximum size of a table (called a data frame) of the R programming 
language. Within R, such a table may have maximally $2^{32}-1$ cells and occupy
less then 2 gigabytes in memory. 
The raw data file will contain parameters and 1000 nLTT statistics values.
Each row will contain the parameter set and these nLTT statistics.
From the constraints of the R programming language, this allows for 40K rows. 
The file with the summarized data will provide summary statistics of the raw
data. Each row will contain a parameter set, summary statistics and other
measurements. See the appendix, chapter 'Data set specifications', for the full list.

>>>>

There will be two data sets produced by this research.
The first data set will be a general balanced data set to chart
the effect of the biological parameters on the nLTT statistic
distribution. The second data set charts the effect of sampling
subspecies (young versus old) and only uses phylogenies in which this sampling
has an effect.

Each data set will consist out of two files, containing raw and summarized 
data respectively. We placed 
an upper limit for this data set's size at the maximum size of a table (called 
a data frame) of the R programming language, in which such a table may 
have maximally $2^{32}-1$ cells and occupy less then 2 gigabytes in memory.
The raw data file will contain parameters and 1000 nLTT statistics values.
Each row will contain the parameter set and these nLTT statistics.
From the constraints of the R programming language, this allows for 40K rows. 
The file with the summarized data will provide summary statistics of the raw
data. Each row will contain a parameter set, summary statistics and other
measurements. See the appendix, chapter 'Data set specifications', for the full list.
